A New Metric for the Analysis of Swarms using Potential Fields

### 2018-10-18 paper.tex
Minors to definitions

\textit{Inter-agent distance} analysis is a basic mechanism for analysing a
swarm in terms of separation of all of the agents with respect to each agent's
visible neighbours. This is different to using the \textit{centroidal} approach,
as the measure is based on agent interactions rather than a resultant structure
which affects the centroid. This technique is the most popular approach to
analysing a swarm's structure. Gazi and Passino use a distance-based analysis
in~\cite{GP:04, GP:11} to identify optimum distribution of agents based upon
different cohesion and repulsion applications. Wu et. al. discuss using
distance-based metrics to evaluate emergent behaviours in swarms based on a
Viscsek model~\cite{WCW:11}. These include calculating the average number of
neighbours for each agent, grouping agents based on numbers of neighbours (to
identify clusters), and calculating the average distance between agents~\cite{WCW:11}.
Schneider and Wildermuth~\cite{SW:03} use a slightly different approach to
measuring performance. They identify the difference in the paths of robots in a
simulated versus a physical implementation and calculate a distance variance
between them.

>>>>

\textit{Inter-agent distance} analysis is a basic mechanism for analysing a
swarm in terms of separation of all of the agents with respect to each agent's
visible neighbours. This is different to using the \textit{centroidal} approach,
as the measure is based on a resultant structure which affects the centroid. 
This technique is the most popular approach to
analysing a swarm's structure. Gazi and Passino use a distance-based analysis
in~\cite{GP:04, GP:11} to identify optimum distribution of agents based upon
different cohesion and repulsion applications. Wu et. al. discuss using
distance-based metrics to evaluate emergent behaviours in swarms based on a
Viscsek model~\cite{WCW:11}. These include calculating the average number of
neighbours for each agent, grouping agents based on numbers of neighbours (to
identify clusters), and calculating the average distance between agents~\cite{WCW:11}.
Schneider and Wildermuth~\cite{SW:03} use a slightly different approach to
measuring performance. They identify the difference in the paths of robots in a
simulated versus a physical implementation and calculate a distance variance
between them.
